---
title: "MemoHR fMRI ROI Activation Data"
author: "Maureen Ritchey"
output:
  html_notebook:
    code_folding: hide
    number_sections: yes
    theme: cosmo
    toc: yes
    toc_float: yes
  html_document:
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_float: yes
---

```{r init, message=FALSE, warning=FALSE, include=FALSE}
library('ggplot2')
library('dplyr') 
library('tidyr')
library('knitr')
library('ez')
options(digits=3)
options(scipen = 999)
```


# Load & Process data
```{r}

savepath <- '../../Analysis/ROI_estimates/'
behavpath <- '../../Data/Behavioral/summary/'

## Load data from csv
### Activation estimates
actdata<-read.csv(paste0(savepath,'cons_ashs_ItemSourceDM_rf_new.csv')) # created with output_roi_cons script in Matlab

### ROI metadata
roidata<-read.csv('../../Analysis/ROI_estimates/roi_info.csv') # contains various labeling schemes for ROIs
actdata <- merge(actdata,roidata,by="roi_file")
rm(roidata)

### Clean up data
# first deal with s21, who had to have EmoK subbed in for EmoM (no EmoM trials)
actdata <- unique(actdata) # remove doubled-up EmoK
tmp <-subset(actdata,subject=="s21" & contrast=="EmoK") # get the EmoK for relabel -> these trial types get averaged anyway
tmp$contrast <- "EmoM"
actdata <- rbind(actdata,tmp) # pull back into main dataframe

### Define new variables
actdata$Emotion <- factor(sapply(actdata$contrast,simplify=TRUE,
                                 function(x) ifelse(grepl('Emo',x),'Emo',
                                                    ifelse(grepl('Neu',x),'Neu',NA))))
actdata <- subset(actdata,!is.na(actdata$Emotion)) # get rid of all other contrasts


actdata$RecMem <- factor(sapply(actdata$contrast,simplify=TRUE,
                                      function(x) ifelse(grepl('R',x),'Rec',
                                                         ifelse(grepl('K',x),'Non-Rec',
                                                                ifelse(grepl('M',x),'Non-Rec',NA)))),
                               levels=c("Rec","Non-Rec"))
actdata$SourceMem <- factor(sapply(actdata$contrast,simplify=TRUE,
                                   function(x) ifelse(grepl('SC',x),'Corr',
                                                      ifelse(grepl('SI',x),'Incorr',NA))))

actdata$BothMem <- factor(ifelse(actdata$RecMem=="Rec" & actdata$SourceMem=="Corr","R+S",
                                 ifelse(actdata$RecMem=="Rec" & actdata$SourceMem=="Incorr","R-S",
                                        ifelse(actdata$RecMem=="Non-Rec","NR",NA))),
                          levels=c("R+S","R-S","NR"))

str(actdata)
kable(table(actdata$BothMem,actdata$subject))

## Create dataframe with 'baseline-corrected' scores, i.e., recollection trial types minus non-recollection
nrbaseline <-
  group_by(actdata,subject,Emotion,roi_file) %>%
  summarize(nr.baseline = mean(activity[RecMem=="Non-Rec"],na.rm=TRUE)) # average over Fam & Miss
actdata.rec <-
  filter(actdata,RecMem=="Rec") %>%
  left_join(nrbaseline)  %>%
  mutate(activity = activity - nr.baseline) # values in actdata.rec are now recollection-related activity
  
## Clean up and save
save(actdata,file=paste0(savepath,'MemoHR_AnatROI_Data_ItemSource.Rdata'))

```

## Report number of voxels in each ROI
```{r numVox}
vox <- group_by(actdata,RegionAP) %>%
  summarize(meanvox=mean(numvox),
            minvox=min(numvox),
            maxvox=max(numvox))
kable(vox)
```

# Plots
## Calculate summary values first
```{r calcSummary}
summarydata.all <- group_by(actdata,subject,Emotion,RecMem,SourceMem,Region,RegionAP,MainRegion,AP) %>%
  summarize(activity=mean(activity)) # This part averages across hemispheres, and fam/miss are averaged into non-rec
meandata.all <- group_by(summarydata.all,Region,RegionAP,MainRegion,AP,Emotion) %>%
  group_by(Emotion,RecMem,SourceMem,Region,RegionAP,MainRegion,AP) %>%
  summarize(meanval=mean(activity,na.rm=TRUE),sdval=sd(activity,na.rm=TRUE),
            sem=sdval/sqrt(length(activity)),
            semmin=meanval-sem,
            semmax=meanval+sem,
            nsubj=length(activity))
meandata.all$EmoMem <- interaction(meandata.all$RecMem,meandata.all$Emotion)
meandata.all$MemMem <- interaction(meandata.all$RecMem,meandata.all$SourceMem)
meandata.all$MemMem <- factor(meandata.all$MemMem,levels=c("Rec.Corr","Rec.Incorr","Non-Rec"))
meandata.all$MemMem[is.na(meandata.all$MemMem)] <- "Non-Rec"

summarydata.rec <- group_by(actdata.rec,subject,Emotion,RecMem,SourceMem,Region,RegionAP,MainRegion,AP) %>%
  summarize(activity=mean(activity))  # This part averages across hemispheres
meandata.rec <- group_by(summarydata.rec,Region,RegionAP,MainRegion,AP,Emotion) %>%
  group_by(Emotion,RecMem,SourceMem,Region,RegionAP,MainRegion,AP) %>%
  summarize(meanval=mean(activity,na.rm=TRUE),sdval=sd(activity,na.rm=TRUE),
            sem=sdval/sqrt(length(activity)),
            semmin=meanval-sem,
            semmax=meanval+sem,
            nsubj=length(activity))
meandata.rec$EmoMem <- interaction(meandata.rec$RecMem,meandata.rec$Emotion)
meandata.rec$MemMem <- interaction(meandata.rec$RecMem,meandata.rec$SourceMem)
meandata.rec$MemMem <- factor(meandata.rec$MemMem,levels=c("Rec.Corr","Rec.Incorr","Non-Rec"))
meandata.rec$MemMem[is.na(meandata.rec$MemMem)] <- "Non-Rec"
```

## Plots with all bars
### Main regions

```{r, fig.height=5, fig.width=10}

# All regions
plotcolors <- c('#d01c8b','#f1b6da',"gray70",'#4dac26','#b8e186',"gray70")

meandata.all %>%
  filter(RegionAP=="Amyg" | RegionAP=="wholeHipp") %>%
  ungroup() %>%
  mutate(RegionAP = factor(RegionAP,levels=c("Amyg","wholeHipp")),
         RegionLabel = factor(ifelse(RegionAP=="wholeHipp","Hipp","Amyg"),
                              levels=c("Amyg","Hipp")),
         MemoryCond = factor(ifelse(MemMem=="Rec.Corr","Rec + Src",ifelse(MemMem=="Rec.Incorr","Rec - Src","Non-Rec")),
                             levels=c("Rec + Src","Rec - Src","Non-Rec")),
         EmoMem = interaction(MemoryCond,Emotion)) %>%
  ggplot(.,aes(x=MemoryCond,y=meanval)) + geom_bar(stat="identity",position="dodge",aes(fill=EmoMem)) +
  geom_errorbar(aes(ymin=meanval-sem,ymax=meanval+sem,width=.25)) + theme_minimal(18) +
  theme(axis.title.x=element_blank()) + facet_grid(.~RegionLabel+Emotion) +
  xlab("Mean activity (au)") + scale_fill_manual(values=plotcolors) +  guides(color=FALSE, fill=FALSE) + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

meandata.all %>%
  filter(RegionAP=="PHC" | RegionAP=="PRC") %>%
  ungroup() %>%
  mutate(RegionAP = factor(RegionAP,levels=c("PRC","PHC")),
         MemoryCond = factor(ifelse(MemMem=="Rec.Corr","Rec + Src",ifelse(MemMem=="Rec.Incorr","Rec - Src","Non-Rec")),
                             levels=c("Rec + Src","Rec - Src","Non-Rec")),
         EmoMem = interaction(MemoryCond,Emotion)) %>%
  ggplot(.,aes(x=MemoryCond,y=meanval)) + geom_bar(stat="identity",position="dodge",aes(fill=EmoMem)) +
  geom_errorbar(aes(ymin=meanval-sem,ymax=meanval+sem,width=.25)) + theme_minimal(18) +
  theme(axis.text.x=element_blank(),axis.title.x=element_blank()) + facet_grid(.~RegionAP+Emotion) +
  xlab("Mean activity (au)") + scale_fill_manual(values=plotcolors) +  guides(color=FALSE, fill=FALSE) + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

```

## Plots with bars subtracting non-recollection

### Single Plots
```{r}
plotcolors <- c('#d01c8b','#f1b6da','#4dac26','#b8e186')

singlePlotROI <- function(roi) {
  meandata.rec %>%
  filter(RegionAP==roi) %>%
  ungroup() %>%
  mutate(MemoryCond = factor(ifelse(MemMem=="Rec.Corr","Rec + Src",ifelse(MemMem=="Rec.Incorr","Rec - Src","Non-Rec")),
                             levels=c("Rec + Src","Rec - Src","Non-Rec")),
         EmoMem = interaction(MemoryCond,Emotion)) %>%
  ggplot(.,aes(x=MemoryCond,y=meanval)) + geom_bar(stat="identity",position="dodge",aes(fill=EmoMem)) +
  geom_errorbar(aes(ymin=meanval-sem,ymax=meanval+sem,width=.25)) + theme_minimal(18) +
  theme(axis.text.x=element_blank(),axis.title.x=element_blank()) + facet_grid(.~Emotion,switch="x") +
  ylab("Recollection-related activity") + scale_fill_manual(values=plotcolors) + guides(color=FALSE) +
    ggtitle(roi) 
}
singlePlotROI_fixedLim <- function(roi,limits) { # fix limits for some plots for better visualization
  singlePlotROI(roi) + ylim(limits)
}

# Plot all regions
singlePlotROI_fixedLim('Amyg',c(-.25,1))
singlePlotROI_fixedLim('wholeHipp',c(-.25,1))
singlePlotROI('PRC')
singlePlotROI('PHC')
```

# Stats

## All regions
```{r, message=FALSE, warning=FALSE}
statdata1 <- subset(actdata.rec,RegionAP=="wholeHipp" | Region=="Amyg"  | Region=="PRC"  | Region=="PHC") 
summary(droplevels(statdata1$Region)) # Note that hemisphere is still included but ezANOVA will average them
anova_mod1<-ezANOVA(statdata1,dv=activity,wid=subject,within=list(BothMem,Emotion,Region),type=3,detailed=TRUE)
print(anova_mod1)

rm(statdata1,anova_mod1)
```

# Follow-up tests
## Amygdala vs PRC
```{r, message=FALSE, warning=FALSE}
statdata1 <- subset(actdata.rec,RegionAP=="PRC" | Region=="Amyg") 
summary(droplevels(statdata1$Region)) # Note that hemisphere is still included but ezANOVA will average them
anova_mod1<-ezANOVA(statdata1,dv=activity,wid=subject,within=list(BothMem,Emotion,Region),type=3,detailed=TRUE)
print(anova_mod1$ANOVA)

statdata2 <- subset(actdata.rec,RegionAP=="PRC" )
anova_mod2<-ezANOVA(statdata2,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod2$ANOVA)

statdata3 <- subset(actdata.rec,Region=="Amyg")
anova_mod3<-ezANOVA(statdata3,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod3$ANOVA)

rm(statdata1,statdata2,statdata3,anova_mod1,anova_mod2,anova_mod3)
```

## PHC vs whole hippocampus
```{r, message=FALSE, warning=FALSE}
statdata1 <- subset(actdata.rec,RegionAP=="wholeHipp" | Region=="PHC") 
summary(droplevels(statdata1$Region)) # Note that hemisphere is still included but ezANOVA will average them
anova_mod1<-ezANOVA(statdata1,dv=activity,wid=subject,within=list(BothMem,Emotion,Region),type=3,detailed=TRUE)
print(anova_mod1$ANOVA)

statdata2 <- subset(actdata.rec,RegionAP=="wholeHipp" )
anova_mod2<-ezANOVA(statdata2,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod2$ANOVA)

statdata3 <- subset(actdata.rec,Region=="PHC")
anova_mod3<-ezANOVA(statdata3,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod3$ANOVA)

rm(statdata1,statdata2,statdata3,anova_mod1,anova_mod2,anova_mod3)
```


## Amygdala vs whole hippocampus
```{r, message=FALSE, warning=FALSE}
statdata1 <- subset(actdata.rec,RegionAP=="wholeHipp" | Region=="Amyg") 
summary(droplevels(statdata1$Region)) # Note that hemisphere is still included but ezANOVA will average them
anova_mod1<-ezANOVA(statdata1,dv=activity,wid=subject,within=list(BothMem,Emotion,Region),type=3,detailed=TRUE)
print(anova_mod1$ANOVA)

statdata2 <- subset(actdata.rec,RegionAP=="wholeHipp" )
anova_mod2<-ezANOVA(statdata2,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod2$ANOVA)

statdata3 <- subset(actdata.rec,Region=="Amyg")
anova_mod3<-ezANOVA(statdata3,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod3$ANOVA)

rm(statdata1,statdata2,statdata3,anova_mod1,anova_mod2,anova_mod3)
```

## Subregions within amygdala
```{r, message=FALSE, warning=FALSE}
statdata1 <- subset(actdata.rec,MainRegion=="Amyg")
summary(droplevels(statdata1$Region))
anova_mod1<-ezANOVA(statdata1,dv=activity,wid=subject,within=list(BothMem,Emotion,Region),type=3,detailed=TRUE)
print(anova_mod1)

statdata2 <- subset(actdata.rec,Region=="BasolatAmyg")
anova_mod2<-ezANOVA(statdata2,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod2$ANOVA)

statdata3 <- subset(actdata.rec,Region=="CentralAmyg")
anova_mod3<-ezANOVA(statdata3,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod3$ANOVA)

statdata4 <- subset(actdata.rec,Region=="CorticalAmyg")
anova_mod4<-ezANOVA(statdata4,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod4$ANOVA)

statdata5 <- subset(actdata.rec,Region=="MedialAmyg")
anova_mod5<-ezANOVA(statdata5,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod5$ANOVA)

rm(statdata1,statdata2,statdata3,statdata4,statdata5,anova_mod1,anova_mod2,anova_mod3,anova_mod4,anova_mod5)

```

## Posterior vs anterior hippocampus
```{r, message=FALSE, warning=FALSE}
statdata1 <- subset(actdata.rec,(RegionAP=="wholeHipp.head" | RegionAP=="wholeHipp.body"))
summary(droplevels(statdata1$RegionAP))
anova_mod1<-ezANOVA(statdata1,dv=activity,wid=subject,within=list(BothMem,Emotion,RegionAP),type=3,detailed=TRUE)
print(anova_mod1$ANOVA)

statdata2 <- subset(actdata.rec,(RegionAP=="wholeHipp.head") )
anova_mod2<-ezANOVA(statdata2,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod2$ANOVA)

statdata3 <- subset(actdata.rec,(RegionAP=="wholeHipp.body" ) )
anova_mod3<-ezANOVA(statdata3,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod3$ANOVA)

rm(statdata1,statdata2,statdata3,anova_mod1,anova_mod2,anova_mod3)

```

## Subregions within posterior hippocampus
```{r, message=FALSE, warning=FALSE}
statdata1 <- subset(actdata.rec,MainRegion=="Hipp")
summary(droplevels(statdata1$Region))
anova_mod<-ezANOVA(statdata1,dv=activity,wid=subject,within=list(BothMem,Emotion,Region),type=3,detailed=TRUE)
print(anova_mod)

statdata2 <- subset(actdata.rec,Region=="CA1")
anova_mod2<-ezANOVA(statdata2,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod2$ANOVA)

statdata3 <- subset(actdata.rec,Region=="CA23DG")
anova_mod3<-ezANOVA(statdata3,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod3$ANOVA)

statdata4 <- subset(actdata.rec,Region=="subiculum")
anova_mod4<-ezANOVA(statdata4,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod4$ANOVA)

rm(statdata1,anova_mod,statdata2,statdata3,statdata4,anova_mod2,anova_mod3,anova_mod4)

```


## PRC vs PHC
```{r, message=FALSE, warning=FALSE}
statdata1 <- subset(actdata.rec,(Region=="PRC" | Region=="PHC") )
anova_mod<-ezANOVA(statdata1,dv=activity,wid=subject,within=list(BothMem,Emotion,Region),type=3,detailed=TRUE)
print(anova_mod$ANOVA)

statdata2 <- subset(actdata.rec,(Region=="PRC") )
anova_mod2<-ezANOVA(statdata2,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod2$ANOVA)

statdata3 <- subset(actdata.rec,Region=="PHC" )
anova_mod3<-ezANOVA(statdata3,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
print(anova_mod3$ANOVA)

rm(statdata1,statdata2,statdata3,anova_mod1,anova_mod2,anova_mod3)

```



# ROI maps

```{r defineMapFunc}
plotROImap <- function(values,colornames) {
  
  ids <- factor(c("Amyg","PRC","PHC","wholeHipp.head","wholeHipp.body","subiculum.body","CA1.body","CA23DG.body","CorticalAmyg","CentralAmyg","MedialAmyg","BasolatAmyg"))
  nid <- length(ids)
  
  # Define polygon coordinates (in this case, 4 each for a rectangle)
  positions <- data.frame(
    id = rep(ids, each = 4),
    order = rep(c(1,2,3,4),nid),
    x = c(1,2,2,1,
          1.5,3,3,1.5,
          3,4,4,3,
          2,3,3,2,
          3,4,4,3,
          3,4,4,3,
          3,4,4,3,
          3,4,4,3,
          1,2,2,1,
          1,2,2,1,
          1,2,2,1,
          1,2,2,1),
    y = c(2,2,3,3,
          1,1,2,2,
          1,1,2,2,
          2,2,3,3,
          2,2,3,3,
          2,2,2.3333,2.3333,
          2.3333,2.3333,2.6666,2.6666,
          2.6666,2.6666,3,3,
          2,2,2.25,2.25,
          2.25,2.25,2.5,2.5,
          2.5,2.5,2.75,2.75,
          2.75,2.75,3,3)
  )
  
  # Calculate midpoint of each poly for label
  positions %>%
    group_by(id) %>%
    summarize(label_x = mean(x),
              label_y = mean(y)) %>%
    left_join(values) %>%
    filter(!is.na(value) & !is.null(value) & value!="NULL") -> values
  
  # Merge id & label info with positions
  datapoly <- merge(values, positions, by=c("id")) %>%
    arrange(id,order) %>%
    ungroup()
  
  # Prettier labels
  values$id[values$id=="wholeHipp.head"] <- "Hipp.ant"
  values$id[values$id=="wholeHipp.body"] <- "Hipp.post"
  
  values$id[values$id=="BasolatAmyg"] <- "Amyg.basolateral"
  values$id[values$id=="MedialAmyg"] <- "Amyg.basomedial"
  values$id[values$id=="CentralAmyg"] <- "Amyg.centromedial"
  values$id[values$id=="CorticalAmyg"] <- "Amyg.cortical"

  # Plot polygons with values coding fill color
  p <- ggplot(datapoly, aes(x=x, y=y)) + geom_polygon(colour="black",aes(fill=value, group=id)) +
    theme_minimal(20) + 
    theme(axis.text = element_blank(),axis.ticks = element_blank()) +
    theme(panel.grid.major = element_blank(),panel.grid.minor=element_blank()) + 
    xlab('') + ylab('') + 
    scale_fill_gradient(low=colornames[1],high=colornames[2],limits=c(0,NA),na.value="gray60",name="effect size") + 
    geom_text(data=values,size=8,aes(label=id,x=label_x,y=label_y))

  return(p)
}
```

## Get stats summary info for plots

```{r, message=FALSE, warning=FALSE}

getAnovaEffectSize <- function(df,effectrow) {
  df <- data.frame(df) # bc ezANOVA hates grouped dataframes
  anova_mod <- ezANOVA(df,dv=activity,wid=subject,within=list(BothMem,Emotion),type=3,detailed=TRUE)
  effectsize <- anova_mod$ANOVA[9][[1]][effectrow]
  return(effectsize)
}

actdata.rec %>%
  filter(RegionAP %in% c("Amyg","wholeHipp.head","wholeHipp.body","PHC","PRC")) %>%
  group_by(RegionAP) %>%
  do(memory = getAnovaEffectSize(.,1),
     source = getAnovaEffectSize(.,2),
     emotion = getAnovaEffectSize(.,3)) %>%
  unnest() -> effectsizes.roi

actdata.rec %>%
  filter(RegionAP %in% c("CorticalAmyg","CentralAmyg","MedialAmyg","BasolatAmyg","CA1.body","CA23DG.body","subiculum.body","wholeHipp.head","PHC","PRC")) %>%
  group_by(RegionAP) %>%
  do(memory = getAnovaEffectSize(.,1),
     source = getAnovaEffectSize(.,2),
     emotion = getAnovaEffectSize(.,3)) %>%
  unnest() -> effectsizes.roi.subreg

print(effectsizes.roi)
print(effectsizes.roi.subreg)

```

## Major subdivisions

```{r, fig.height=2, fig.width=6, message=FALSE, warning=FALSE}
map.mem <- data.frame(id=as.character(effectsizes.roi$RegionAP),value=as.numeric(effectsizes.roi$memory))
plotROImap(map.mem,c('white','orange')) + ggtitle("Recollection-related activity")
map.emo <- data.frame(id=as.character(effectsizes.roi$RegionAP),value=as.numeric(effectsizes.roi$emotion))
plotROImap(map.emo,c('white','tomato')) + ggtitle("Effect of emotion on recollection-related activity")
map.src <- data.frame(id=as.character(effectsizes.roi$RegionAP),value=as.numeric(effectsizes.roi$source))
plotROImap(map.src,c('white','skyblue1')) + ggtitle("Effect of context encoding on recollection-related activity")

```

## With subregions
```{r, fig.height=2, fig.width=6, message=FALSE, warning=FALSE}
map.mem2 <- data.frame(id=as.character(effectsizes.roi.subreg$RegionAP),value=as.numeric(effectsizes.roi.subreg$memory))
plotROImap(map.mem2,c('white','orange')) + ggtitle("Recollection-related activity")
map.emo2 <- data.frame(id=as.character(effectsizes.roi.subreg$RegionAP),value=as.numeric(effectsizes.roi.subreg$emotion))
plotROImap(map.emo2,c('white','tomato')) + ggtitle("Effect of emotion on recollection-related activity")
map.src2 <- data.frame(id=as.character(effectsizes.roi.subreg$RegionAP),value=as.numeric(effectsizes.roi.subreg$source))
plotROImap(map.src2,c('white','skyblue1')) + ggtitle("Effect of context encoding on recollection-related activity")

```
