---
title: "MemoHR fMRI ROI - Predict memory outcomes"
author: "Maureen Ritchey"
output:
  html_notebook:
    code_folding: hide
    number_sections: yes
    theme: cosmo
    toc: yes
    toc_depth: 4
    toc_float: yes
  html_document:
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r init, message=FALSE, warning=FALSE, include=FALSE}
library('tidyverse')
library('ez')
library('stringr')
library('lme4')
library('visreg')
library('lattice')
options(digits=3)
options(scipen = 999)
```


# Load & Process data
```{r, message=FALSE, warning=FALSE}

savepath <- '../../Analysis/ROI_estimates/'
behavpath <- '../../Data/Behavioral/summary/'

## Load data from csv
### Activation estimates
actdata<-read.csv(paste0(savepath,'cons_ashs_betas_ItemSourceDM_rf_new_ST.csv')) # created with output_roi_cons script in Matlab

### ROI metadata
roidata<-read.csv('../../Analysis/ROI_estimates/roi_info.csv') # contains various labeling schemes for ROIs
actdata <- merge(actdata,roidata,by="roi_file")
rm(roidata)
actdata$RegionAP <- droplevels(actdata$RegionAP)
actdata$Region <- droplevels(actdata$Region)

## Get condition info from beta descriptions
actdata$contrast <- as.character(actdata$contrast)
actdata %>%
  mutate(emotion = factor(str_sub(contrast,29,31))) %>%
  filter(emotion!="Oth") %>%
  mutate(session = factor(str_sub(contrast,26,26)),
         emotion = factor(str_sub(contrast,29,31)),
         memory = str_sub(contrast,32,35)) %>%
  separate(memory,c("memory","tmp"),sep="_")  %>% # this is the line that throws the "too few values" warning - not a real issue
  select(roi_file,subject,contrast,activity,Region,Hemisphere,RegionAP,emotion,session,memory) -> actdata

actdata %>%
  mutate(memory = factor(ifelse(memory=="-SI","R-SI",memory),
                         levels=c("R-SC","R-SI","K","M")),
         recmem = factor(ifelse(memory=="R-SI"|memory=="R-SC","Rec","Non-Rec"),levels=c("Non-Rec","Rec")),
         sourcemem = factor(ifelse(memory=="R-SI","SI",
                                ifelse(memory=="R-SC","SC",NA)),levels=c("SI","SC"))) -> actdata 
str(actdata)

actdata %>%
  group_by(subject,roi_file) %>%
  mutate(meanact = mean(activity),
         sdact = sd(activity),
         activity.z = (activity - meanact)/sdact,
         activity.z = ifelse(abs(activity.z)>3,NA,activity.z)) -> actdata # remove outliers

## Average over hemispheres
actdata %>%
  group_by(subject,RegionAP,session,emotion,memory,recmem,sourcemem,contrast) %>%
  summarize(activity = mean(activity.z))  -> avgdata 

## Cast RegionAP to columns
avgdata %>%
  spread(RegionAP,activity) -> avgdata.roi

## Define colors
emocolor <- '#d01c8b'
neucolor <- '#4dac26'

```

# Basic plots
## Sanity checks

To make sure averaged results look roughly the way that I expect from prior analyses

```{r}

avgdata %>%
  group_by(subject,memory,emotion,RegionAP) %>%
  summarize(activity = mean(activity)) %>%
  ggplot(aes(x=memory,y=activity,color=emotion)) + geom_boxplot() + facet_grid(.~RegionAP)

```

To check out distributions

```{r}
avgdata.roi %>%
  ggplot(aes(x=Amyg,y=PRC)) + facet_grid(.~recmem) + stat_smooth(method="lm",se=FALSE) + geom_point(aes(color=subject)) 

```



# Regression predicting recollection outcomes
```{r, message=FALSE, warning=FALSE}
avgdata.roi %>%
  filter(!is.na(recmem)) %>%
  filter(!is.na(Amyg+PRC+PHC+wholeHipp+wholeHipp.head+wholeHipp.body)) -> avgdata.roi.rec # this limits to trials with intact data
```

## Each region alone
```{r}

# Set up base models, no emotion
intonly <- glmer(recmem ~ (1|subject/session),data=avgdata.roi.rec,family=binomial)

amyg <- glmer(recmem ~ Amyg + (1|subject/session),data=avgdata.roi.rec,family=binomial)
hipp <- glmer(recmem ~ wholeHipp + (1|subject/session),data=avgdata.roi.rec,family=binomial)
prc <- glmer(recmem ~ PRC + (1|subject/session),data=avgdata.roi.rec,family=binomial)
phc <- glmer(recmem ~ PHC + (1|subject/session),data=avgdata.roi.rec,family=binomial)
ahipp <- glmer(recmem ~ wholeHipp.head + (1|subject/session),data=avgdata.roi.rec,family=binomial)

anova(intonly,amyg)
anova(intonly,hipp)
anova(intonly,prc)
anova(intonly,phc)

# make sure that the amygdala~memory effect is modulated by emotion (which it should be)
amygemo <- glmer(recmem ~ Amyg + emotion + (1|subject/session),data=avgdata.roi.rec,family=binomial)
amygemoxx <- glmer(recmem ~ Amyg*emotion + (1|subject/session),data=avgdata.roi.rec,family=binomial)
anova(amygemo,amygemoxx)

# Set up rest of base models, with emotion
hippemo <- glmer(recmem ~ wholeHipp + emotion + (1|subject/session),data=avgdata.roi.rec,family=binomial)
prcemo <- glmer(recmem ~ PRC + emotion + (1|subject/session),data=avgdata.roi.rec,family=binomial)
phcemo <- glmer(recmem ~ PHC + emotion + (1|subject/session),data=avgdata.roi.rec,family=binomial)
ahippemo <- glmer(recmem ~ wholeHipp.head + emotion + (1|subject/session),data=avgdata.roi.rec,family=binomial)

hippemoxx <- glmer(recmem ~ wholeHipp*emotion + (1|subject/session),data=avgdata.roi.rec,family=binomial)
prcemoxx <- glmer(recmem ~ PRC*emotion + (1|subject/session),data=avgdata.roi.rec,family=binomial)
phcemoxx <- glmer(recmem ~ PHC*emotion + (1|subject/session),data=avgdata.roi.rec,family=binomial)
ahippemoxx <- glmer(recmem ~ wholeHipp.head*emotion + (1|subject/session),data=avgdata.roi.rec,family=binomial)
 

```

## Amyg combined with others

### PRC
#### Additive effects of amygdala & PRC
```{r}

amygprcemo <- glmer(recmem ~ Amyg*emotion + PRC*emotion + (1|subject/session),data=avgdata.roi.rec,family=binomial)
anova(amygemoxx,amygprcemo) # additive effect of PRC
anova(prcemoxx,amygprcemo) # additive effect of Amyg

```

Conclusion: Subsequent recollection is predicted well by amygdala and its interaction with emotion, but it improves when PRC is added. 

#### Interactive effects of amygdala & PRC
```{r}

amygprcxxemo <- glmer(recmem ~ Amyg*emotion + PRC*emotion + Amyg*PRC + (1|subject/session),data=avgdata.roi.rec,family=binomial)
anova(amygprcemo,amygprcxxemo)

amygprcemoxxx <- glmer(recmem ~ Amyg*emotion*PRC + (1|subject/session),data=avgdata.roi.rec,family=binomial)
anova(amygprcxxemo,amygprcemoxxx)

```
Conclusion: Knowing the interaction of amygdala & PRC improves the model. There is not a three-way interaction with emotion (i.e., the amyg-PRC interaction is similar for negative & neutral).

#### Visualization
```{r, fig.height=2, fig.width=4}

trellis.par.set(strip.background=list(col="gray90"))
visreg(amygprcxxemo, "PRC", scale="response",by="Amyg",cond=list(emotion="Emo"),rug=2,
       xlab="PRC activity", ylab="P(subsequent recollection)",
       breaks=c(-1,0,1),strip.names=c("low amygdala activity",'medium amygdala activity','high amygdala activity'),
       line=list(col=c(emocolor)))

trellis.par.set(strip.background=list(col="gray90"))
visreg(amygprcxxemo, "PRC", scale="response",by="Amyg",cond=list(emotion="Neu"),rug=2,
       xlab="PRC activity", ylab="P(subsequent recollection)",
       breaks=c(-1,0,1),strip.names=c("low amygdala activity",'medium amygdala activity','high amygdala activity'),
       line=list(col=c(neucolor)))

# can't seem to change rug color separately from line color - creating another version to include in overlay
trellis.par.set(strip.background=list(col="gray90"))
visreg(amygprcxxemo, "PRC", scale="response",by="Amyg",cond=list(emotion="Neu"),rug=2,
       xlab="PRC activity", ylab="P(subsequent recollection)",
       breaks=c(-1,0,1),strip.names=c("low amygdala activity",'medium amygdala activity','high amygdala activity'),
       line=list(col=c("gray50")))

```

### Hippocampus
```{r, fig.height=2, fig.width=4}

amyghipp <- glmer(recmem ~ Amyg + wholeHipp + (1|subject/session),data=avgdata.roi.rec,family=binomial)
amyghippxx <- glmer(recmem ~ Amyg*wholeHipp  + (1|subject/session),data=avgdata.roi.rec,family=binomial)
anova(amyghipp,amyghippxx)

amyghippemo <- glmer(recmem ~ Amyg*emotion + wholeHipp*emotion + (1|subject/session),data=avgdata.roi.rec,family=binomial)
amyghippemoxx <- glmer(recmem ~ Amyg*wholeHipp*emotion + (1|subject/session),data=avgdata.roi.rec,family=binomial)
anova(amyghippemo,amyghippemoxx)

visreg(amyghippxx, "wholeHipp", scale="response",by="Amyg",rug=2,xlab="Hippocampal activity", ylab="P(subsequent recollection)",
       breaks=c(-1,0,1),strip.names=c("low amygdala activity",'medium amygdala activity','high amygdala activity'))
# visreg(amyghippxx, "Amyg", scale="response",by="wholeHipp",rug=2,xlab="Amygdala activity", ylab="P(subsequent recollection)",
#        breaks=c(-1,0,1))


```

The amygdala-hippocampal interaction is not significant, with or without emotion.


# Regression predicting source memory
```{r}
avgdata.roi %>%
  filter(!is.na(sourcemem))  %>%
  filter(!is.na(Amyg+PRC+PHC+wholeHipp+wholeHipp.head+wholeHipp.body)) -> avgdata.roi.src # this limits to only recollection trials with intact data
```

## Each region alone
```{r}

intonly <- glmer(sourcemem ~  (1|subject/session),data=avgdata.roi.src,family=binomial)

amyg <- glmer(sourcemem ~ Amyg + (1|subject/session),data=avgdata.roi.src,family=binomial)
hipp <- glmer(sourcemem ~ wholeHipp + (1|subject/session),data=avgdata.roi.src,family=binomial)
prc <- glmer(sourcemem ~ PRC + (1|subject/session),data=avgdata.roi.src,family=binomial)
phc <- glmer(sourcemem ~ PHC + (1|subject/session),data=avgdata.roi.src,family=binomial)

anova(intonly,amyg)
anova(intonly,hipp)
anova(intonly,prc)
anova(intonly,phc)

```

## Amyg combined with others
### Hippocampus
```{r}

amyghipp <- glmer(sourcemem ~ Amyg + wholeHipp + (1|subject/session),data=avgdata.roi.src,family=binomial)
amyghippxx <- glmer(sourcemem ~ Amyg*wholeHipp  + (1|subject/session),data=avgdata.roi.src,family=binomial)
anova(amyghipp,amyghippxx)

amyghippemo <- glmer(sourcemem ~ Amyg*emotion + wholeHipp*emotion + (1|subject/session),data=avgdata.roi.src,family=binomial)
amyghippemo2 <- glmer(sourcemem ~ Amyg*emotion + wholeHipp*emotion + Amyg*wholeHipp  + (1|subject/session),data=avgdata.roi.src,family=binomial)
anova(amyghippemo,amyghippemo2)

amyghippemoxx <- glmer(sourcemem ~ Amyg*wholeHipp*emotion  + (1|subject/session),data=avgdata.roi.src,family=binomial)
anova(amyghippemo2,amyghippemoxx) # does adding the 3-way interaction add anything beyond the simple amyg-hipp intx?

```

Conclusion: Amygdala & hippocampus interact to support subsequent source memory, but there's not a three-way interaction with emotion.

### Visualization
```{r, fig.height=2, fig.width=4}
trellis.par.set(strip.background=list(col="gray90"))
visreg(amyghippemoxx, "wholeHipp", scale="response",by="Amyg",cond=list(emotion="Emo"),rug=2,
       xlab="Hippocampal activity", ylab="P(subsequent source)",
       breaks=c(-1,0,1),strip.names=c("low amygdala activity",'medium amygdala activity','high amygdala activity'),
       line=list(col=emocolor))

trellis.par.set(strip.background=list(col="gray90"))
visreg(amyghippemoxx, "wholeHipp", scale="response",by="Amyg",cond=list(emotion="Neu"),rug=2,
       xlab="Hippocampal activity", ylab="P(subsequent source)",
       breaks=c(-1,0,1),strip.names=c("low amygdala activity",'medium amygdala activity','high amygdala activity'),
       line=list(col=neucolor))

# can't seem to change rug color separately from line color - creating another version to include in overlay
trellis.par.set(strip.background=list(col="gray90"))
visreg(amyghippemoxx, "wholeHipp", scale="response",by="Amyg",cond=list(emotion="Neu"),rug=2,
       xlab="Hippocampal activity", ylab="P(subsequent source)",
       breaks=c(-1,0,1),strip.names=c("low amygdala activity",'medium amygdala activity','high amygdala activity'),
       line=list(col="gray50"))
```
